A general Nullstellensatz for generalized spaces

### 2019-03-11 paper-qcoh.tex
Further statements

% Set[T] einführen

@@

% XXX corollary: function spaces

% XXX prove higher-order characterization?

>>>>

% XXX Set[T] einführen

@@

\begin{cor}Let~$\TT$ be a geometric theory. Let~$\{\vec x\_ \varphi\}$
and~$\{\vec y\_ \psi\}$ be geometric formulas in given contexts. Then,
internally to~$\Set[\TT]$, the canonical map from the set of equivalence classes
of~$\ul{\TT}/U$-provably$^\star$ functional geometric$^\star$ formulas
from~$\{\vec x\_ \varphi\}$ to~$\{\vec y\_ \psi\}$ to the set of maps~$\{(\vec y)
\,|\, \psi \}^{\{(\vec x) \,|\, \varphi\}}$ is a bijection.
\end{cor}

% XXX fill in proof

\begin{thm}\label{thm:higher-order-nullstellensatz}
Let~$\TT$ be a geometric theory. Then, internally to~$\Set[\TT]$, for any
higher-order geometric$^\star$ sequent~$\sigma$ over the signature
of~$\ul{\TT}/U$, the following statements are equivalent:
\begin{enumerate}
\item The sequent~$\sigma$ holds for~$U_\TT$.
\item The sequent~$\sigma$ is provable$^\star$ modulo~$\TT/U_\TT$ in geometric
higher-order logic.
\end{enumerate}
\end{thm}

% XXX fill in proof

\begin{thm}\label{thm:higher-order-characterization}
Let~$\TT$ be a geometric theory. Let~$\alpha$ be a higher-order formula over
the signature of~$\TT$. Then the following statements are equivalent:
\begin{enumerate}
\item The formula~$\alpha$ holds for~$U_\TT$.
\item The formula~$\alpha$ is provable in higher-order intuitionistic logic
modulo the axioms of~$\TT$ and the additional axiom scheme~XXX.
\end{enumerate}
\end{thm}

% XXX fill in proof
